---
title: "Office Hour 1"
author: "Kieran Healy"
date: "1/20/2022"
output: html_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup

```{r}
library(tidyverse)
library(socviz)
library(gapminder)
```


## Day One sample exercises

- The office hour is primarily for any questions you might have, but I'll also work through the following these exercises if you want to give them a try. 

1. Use RStudio to create an RMarkdown file named something like `office_01.Rmd`
2. Set up your file with a code chunk that loads the `tidyverse`, and `gapminder` packages.
3. Then use R to draw these plots:

```{r plot-samples-1, fig.cap = "GDP and Life Expecancy 1", echo = FALSE, message = FALSE}

ggplot(data = gapminder,  
     mapping = aes(x = gdpPercap, y = lifeExp)) + 
     geom_point() + 
     geom_smooth() + 
     labs(x = "GDP Per Capita",
     y = "Life Expectancy")

```


```{r plot-samples-2, fig.cap = "GDP and Life Expecancy 2", echo = FALSE, message = FALSE}

ggplot(data = gapminder,  
     mapping = aes(x = gdpPercap, y = lifeExp)) + 
     geom_point() + 
     geom_smooth() + 
     scale_x_log10(labels = scales::dollar) + 
     labs(x = "GDP Per Capita (log scale)",
     y = "Life Expectancy")

```

```{r plot-samples-3, fig.cap = "GDP and Life Expecancy 3", echo = FALSE, message = FALSE}
ggplot(data = gapminder,  
     mapping = aes(x = gdpPercap, y = lifeExp, size = pop)) + 
     geom_point() + 
     geom_smooth(method = "lm") + 
     scale_x_log10(labels = scales::dollar) + 
     labs(x = "GDP Per Capita (log scale)",
     y = "Life Expectancy", size = "Population")

```

```{r plot-samples-4, fig.cap = "GDP and Life Expectancy 4", echo = FALSE, message = FALSE}
ggplot(data = gapminder,  
     mapping = aes(y = gdpPercap, x = lifeExp, size = pop)) + 
     geom_point(color = "gray20", alpha = 0.3) + 
     geom_smooth() + 
     scale_y_log10(labels = scales::dollar) + 
     labs(y = "GDP Per Capita (log scale)",
     x = "Life Expectancy", size = "Population")

```

- Think also about how these plots might be further improved.




